Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-11-02 pkg/disttree/inst/draft/rejoinder.Rnw
small touch-ups in abstract/intro
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2372 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4eb56ab7907fb1c328e898785cfe442533ec4c10
final Z revision of main manuscript, adapting much of the discussion further touch-ups in remaining materials
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2375 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: a394dd57fb692b04399df40ba94b573455f36c1f

\item \emph{Section~4: Discussion.}\\
The concluding section of the main manuscript has been rewritten and
extended to regarding discussion of: variable selection, tuning parameters,
distributional specifications (referring to Supplement~A), and regional
differences (referring to Supplement~B).

@@

\vspace*{-2.8cm}
\hspace*{-0.3cm} 
\includegraphics[width = 0.23\textwidth]{signature-Schlosser}

@@

Applying the Law of Large Numbers it can be shown that random forests do not overfit 
as the number of trees increases (Breiman 2001, Hastie et al.\ 2001, 
Biau et al.\ 2016). Therefore, in principle, forests can be built with a very
large number of trees as this cannot deteriorate the predictions.
However, ``[\dots] the computational cost for inducing a forest increases linearly 
with the number of trees, so a good choice results from a trade-off between 
computational complexity and accuracy'' (Biau et al.\ 2016, p.~205). Following this 
advice, we decided to build forests consisting of 100 trees. Increasing this number
further would not change the results much.

Moreover, Hastie et al.\ (2001, p.~596) recommend to build trees of maximal depth:
``Our experience is that using full-grown trees seldom costs much, and 
results in one less tuning parameter.''
Thus, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) should be kept low
-- but in our context large enough for estimating the distribution parameters
reasonably well. Thus, in our application we have set \texttt{minsplit} to 50 and
\texttt{minbucket} to 20. The significance level \texttt{alpha} (for early stopping
upon non-significance) is set to 1, thus disabling any early stopping.
These tuning parameters are now also listed in the main manuscript in Sections~3.2.
and discussed in Section~4.

@@

For each new observation $z$ the corresponding 
parameter vector $\hat{\Theta}(z)$ can be calculated following 
the given formula. But you are right, this is equivalent to simply
obtaining the parameter vector that has been estimated in the 
corresponding node when learning the tree. This is now also
explained at the end of Section~2.2.

@@

Overall, the covariates selected by the distributional forest do not provide too 
much insights but show that the prespecified GAMLSS model contains an appropriate 
subset of all available covariates.

@@

We completely agree with you that GAMLSS are tremendously useful,
especially in situations where an interpretable but still
well-performing model is needed. The intention of our work is not
to present distributional forests as a replacement of GAMLSS but
rather as a complementing technique for the distributional regression
toolbox. Much like random forests and GAMs are complements in
the conditional mean regression toolbox.

@@

We have adapted our manuscript in Section~1 and Section~4, \textit{Variable Selection}, 
to reflect that we focus on forecasting skill in a large number of 
models -- and not so much on interpretation.

@@

As pointed out by Breiman (2001), random forests are very robust and do not overfit, 
not even for a high number of trees. However, computational costs increase 
linearly with the number of trees (Biau et al.\ 2016).
Therefore, we followed their recommendations of choosing a high number of
trees, but still small enough to keep the computation time at
a reasonable level. For this, 100 is a commonly-used number of trees.
Tuning parameters of distributional forests, including the number of 
trees (\texttt{ntree}), are now discussed in Section~4 
of the main manuscript.

@@

%\item[] Goicoa, T., Adin, A., Ugarte, M. D. and Hodges, J. S. (2017). 
%In Spatio-Temporal Disease Mapping Models, Identifiability Constraints 
%Affet PQL and INLA Results, \textit{Stochastic Environmental Research 
%and Risk Assessment} p. to appear.

%\item[] Ugarte, M. D., Adin, A. and Goicoa, T. (2017). One-Dimensional, 
%Two-Dimensional, and Three-Dimensional B-Splines to Specify Space-Time 
%Interactions in Bayesian Disease Mapping: Model Fitting and Model 
%Identifiability, \textit{Spatial Statistics} p. to appear.

@@

%%%%%%%%%
% references used in answers
\item[] Gneiting, T., Raftery, A. E., Westveld III, A. H. and Goldman, T. (2005). 
Calibrated Probabilistic Forecasting Using Ensemble Model Output Statistics and 
Minimum CRPS Estimation,
\textit{Monthly Weather Review} \textbf{133, 5}: 1098--1118.

@@

%\item[] Hofner, B., Boccuto, L. and Goeker, M. (2015). 
%Controlling false discoveries in high-dimensional situations: Boosting 
%with stability selection,
%\textit{BMC Bioinformatics} \textbf{16:144}.

@@

\item[] Rasp, S., Lerch, S. (2018). Neural Networks for Post-Processing Ensemble
Weather Forecasts, \textit{Montly Weather Review}, NA.
%doi:\href{https://doi.org/10.1175/MWR-D-18-0187.1}{10.1175/MWR-D-18-0187.1}.

\item[] M{\"u}ller, M. D. (2011): Effects of Model Resolution and Statistical
Postprocessing on Shelter Temperature and Wind Forecasts,
\textit{Journal of Applied Meteorology and Climatology} 
\textbf{50 8}: 1627--1636.
%doi:10.1175/2011JAMC2615.1

\item[] Stidd, C. K. (1973). Estimating the Precipitation Climate,
\textit{Water Resources Research}, \textbf{9, 5}: 1235--1241.
%doi:10.1029/wr009i005p01235
\end{itemize}

>>>>

\item \emph{Section~4: Discussion.}\\
The concluding section of the main manuscript has been rewritten and
extended regarding discussion of: variable selection, tuning parameters,
distributional specifications (referring to Supplement~A), and regional
differences (referring to Supplement~B).

@@

\vspace*{-2.8cm}
\hspace*{-0.3cm} 
%\includegraphics[width = 0.23\textwidth]{signature-Schlosser}

@@

Applying the Law of Large Numbers it can be shown that random forests do not overfit 
as the number of trees increases (Breiman 2001, Hastie et al.\ 2001, 
Biau and Scornet 2016). Therefore, in principle, forests can be built with a very
large number of trees as this cannot deteriorate the predictions.
However, ``[\dots] the computational cost for inducing a forest increases linearly 
with the number of trees, so a good choice results from a trade-off between 
computational complexity and accuracy'' (Biau and Scornet 2016, p.~205). Following this 
advice, we decided to build forests consisting of 100 trees. Increasing this number
further would not change the results much.

Moreover, Hastie et al.\ (2001, p.~596) recommend to build trees of maximal depth:
``Our experience is that using full-grown trees seldom costs much, and 
results in one less tuning parameter.''
Thus, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) should be kept low
-- but in our context large enough for estimating the distribution parameters
reasonably well. Thus, in our application we have set \texttt{minsplit} to 50 and
\texttt{minbucket} to 20. The significance level \texttt{alpha} (for early stopping
upon non-significance) is set to 1, thus disabling such early stopping.
These tuning parameters are now also listed in the main manuscript in Sections~3.2.
and discussed in Section~4.

@@

For each new observation $z$ the corresponding 
parameter vector $\hat{\Theta}(z)$ can be calculated following 
the given formula. But you are right, this is equivalent to simply
obtaining the parameter vector that has been estimated in the 
corresponding node when learning the tree. This is now emphasized
in the last paragraph of Section~2.2.

@@

Overall, the covariates selected by the distributional forest do not provide 
new meteorological insights but show that the prespecified GAMLSS model contains an appropriate 
subset of all available covariates.

@@

We completely agree with you that GAMLSS are tremendously useful,
especially in situations where an interpretable but still
well-performing model is needed. The intention of our work is not
to present distributional forests as a replacement of GAMLSS but
rather as a complementing technique for the distributional regression
toolbox. Much like random forests and GAMs are complements for
conditional mean regression.

@@

We have adapted our introduction (Section~1) and discussion (Section~4)
to better reflect these aspects.

@@

As pointed out by Breiman (2001), random forests are very robust and do not overfit, 
not even for a high number of trees. However, computational costs increase 
linearly with the number of trees (Biau and Scornet, 2016).
Therefore, we followed their recommendations of choosing a high number of
trees, but still small enough to keep the computation time at
a reasonable level. For this, 100 is a commonly-used number of trees.
Tuning parameters of distributional forests, including the number of 
trees (\texttt{ntree}), are now discussed in Section~4 
of the main manuscript.

@@

\item[] Gneiting, T., Raftery, A. E., Westveld III, A. H. and Goldman, T. (2005). 
Calibrated Probabilistic Forecasting Using Ensemble Model Output Statistics and 
Minimum CRPS Estimation,
\textit{Monthly Weather Review} \textbf{133, 5}: 1098--1118.

@@

\item[] M{\"u}ller, M. D. (2011): Effects of Model Resolution and Statistical
Postprocessing on Shelter Temperature and Wind Forecasts,
\textit{Journal of Applied Meteorology and Climatology} 
\textbf{50, 8}: 1627--1636.
%doi:10.1175/2011JAMC2615.1

\item[] Rasp, S., Lerch, S. (2018). Neural Networks for Post-Processing Ensemble
Weather Forecasts, \textit{Montly Weather Review}, \textbf{146, 11}:, 3885--3900.
%doi:\href{https://doi.org/10.1175/MWR-D-18-0187.1}{10.1175/MWR-D-18-0187.1}.

@@

\item[] Stidd, C. K. (1973). Estimating the Precipitation Climate,
\textit{Water Resources Research}, \textbf{9, 5}: 1235--1241.
%doi:10.1029/wr009i005p01235

@@
